%%
%% This is file `./samples/longsample.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% apa7.dtx  (with options: `longsample')
%% ----------------------------------------------------------------------
%% 
%% apa7 - A LaTeX class for formatting documents in compliance with the
%% American Psychological Association's Publication Manual, 7th edition
%% 
%% Copyright (C) 2021 by Daniel A. Weiss <daniel.weiss.led at gmail.com>
%% 
%% This work may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License (LPPL), either
%% version 1.3c of this license or (at your option) any later
%% version.  The latest version of this license is in the file:
%% 
%% http://www.latex-project.org/lppl.txt
%% 
%% Users may freely modify these files without permission, as long as the
%% copyright line and this statement are maintained intact.
%% 
%% This work is not endorsed by, affiliated with, or probably even known
%% by, the American Psychological Association.
%% 
%% ----------------------------------------------------------------------
%% 
\documentclass[stu, floatsintext, helv]{apa7}

\usepackage{lipsum}

\usepackage{enumitem}

\usepackage[american]{babel}

\usepackage{tikz}
\usetikzlibrary{shapes.geometric, arrows, positioning, calc}
\usepackage{csquotes}
\usepackage{pdfpages}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{makecell}
\usepackage{placeins}
\usepackage[style=apa,backend=biber]{biblatex}
\addbibresource{bibliography.bib}


\renewcommand\theadalign{cc} % Zentriert den Text in der Kopfzeile
\renewcommand\theadfont{\bfseries} % Fettgedruckter Text für die Kopfzeile
\renewcommand\cellalign{l} % Setzt die Standardausrichtung von makecell auf linksbündig


\title{Gender Differences in the Impact of Gamification Elements on Performance and Anxiety}
\shorttitle{Gender Differences in the Impact of Gamification Elements}

%\authorsnames{Robin Gebert, Nadine Koch, Niklas Meißner, Jun.-Prof. Dr. rer. nat. Maria Wirzberger}
%\authorsaffiliations{University of Stuttgart}
\author{Robin Gebert}
\authorsaffiliations{University of Stuttgart}
\course{Informatik - B.A. (Lehramt)}
\professor{Jun.-Prof. Dr. rer. nat. Maria Wirzberger}
\advisor{Nadine Nicole Koch, M.Sc.\newline\noindent Niklas Meißner, M.Sc.}
\startdate{06. Mai 2024}
\enddate{06. September 2024}

\leftheader{Gebert}

\abstractGerman{Diese Bachelorarbeit untersucht die Auswirkungen verschiedener Gamification-Elemente auf Leistung und Angst in digitalen Lernumgebungen, mit einem besonderen Fokus auf Geschlechterunterschiede. Trotz der breiten Anwendung von Gamification in Bildungstechnologien ist das Verständnis darüber, wie individuelle Faktoren wie Geschlecht diese Effekte beeinflussen, begrenzt. Die Studie verwendet ein 2$\times$8 faktorielles Design, um die Interaktionen zwischen Gamification-Elementen und Geschlecht zu analysieren, wobei 117 Teilnehmer aus verschiedenen Studiengängen rekrutiert wurden. Die Ergebnisse zeigen, dass verschiedene Gamification-Elemente die Leistung und Angst unterschiedlich beeinflussen, jedoch waren diese Gruppenunterschiede überwiegend deskriptiv und nicht signifikant. Diese Erkenntnisse deuten darauf hin, dass die Anpassung von Gamification-Strategien an geschlechtsspezifische Reaktionen potenziell die Effektivität von digitalen Lernumgebungen verbessern könnte. Die Studie betont die Notwendigkeit weiterer Forschungen, um die Beziehung zwischen Gamification, Geschlecht und Lernausgängen tiefer zu verstehen.}
\keywordsGerman{Gamification, Geschlecht, Intelligente Tutorielle Systeme, Leistung, Angst}

\abstractEnglish{This bachelor thesis explores the effects of various gamification elements on performance and anxiety in digital learning environments, with a specific focus on gender differences. Despite the widespread application of gamification in educational technologies, understanding of how individual factors such as gender influence these effects remains limited. The study employed a 2$\times$8 factorial design to analyze interactions between gamification elements and gender, recruiting 117 participants from various degree programs. Findings indicate that different gamification elements variably affect performance and anxiety, however, these group differences were predominantly descriptive and not significant effects. These insights suggest that tailoring gamification strategies to gender-specific responses could potentially enhance the effectiveness of digital learning environments. The study underscores the need for further research to deepen understanding of the relationship between gamification, gender, and learning outcomes.}
\keywordsEnglish{Gamification, Gender, Intelligent tutoring systems, Performance, Anxiety}

%%
%%\authornote{
%%   \addORCIDlink{Daniel A. Weiss}{0000-0000-0000-0000}
%%
%%  Correspondence concerning this article should be addressed to Daniel A. Weiss, Department of Educational Psychology, Counseling and
%%  Special Education, A University Somewhere, 123 Main St., Oneonta, NY
%%  13820.  E-mail: daniel.weiss.led@gmail.com}
%%
\begin{document}
\maketitle


%\input{content/introduction.tex}
\input{content/theoretical_background.tex}
\input{content/hypotheses.tex}
\input{content/methods.tex}
\input{content/results.tex}
\input{content/discussion.tex}

\subsection*{Acknowledgements}
We acknowledge the support of the German Research Foundation (DFG; DFG reference number UP 31/1) for funding the Stuttgart Research Focus Interchange Forum for Reflecting on Intelligent Systems (IRIS).
This research was further supported by the Ministry of Science, Research, and the Arts (MWK) Baden-Württemberg, Germany, within the Artificial Intelligence Software Academy (AISA; reference number Az. 7542.2-9-47.10/36/2).

\printbibliography

\end{document}

%% 
%% Copyright (C) 2021 by Daniel A. Weiss <daniel.weiss.led at gmail.com>
%% 
%% This work may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License (LPPL), either
%% version 1.3c of this license or (at your option) any later
%% version.  The latest version of this license is in the file:
%% 
%% http://www.latex-project.org/lppl.txt
%% 
%% Users may freely modify these files without permission, as long as the
%% copyright line and this statement are maintained intact.
%% 
%% This work is not endorsed by, affiliated with, or probably even known
%% by, the American Psychological Association.
%% 
%% 
%% This work is "maintained" (as per LPPL maintenance status) by
%% Daniel A. Weiss.
%% 
%% This work consists of the file  apa7.dtx
%% and the derived files           apa7.ins,
%%                                 apa7.cls,
%%                                 apa7.pdf,
%%                                 README,
%%                                 APA7american.txt,
%%                                 APA7british.txt,
%%                                 APA7dutch.txt,
%%                                 APA7english.txt,
%%                                 APA7french.txt,
%%                                 APA7german.txt,
%%                                 APA7ngerman.txt,
%%                                 APA7greek.txt,
%%                                 APA7czech.txt,
%%                                 APA7turkish.txt,
%%                                 APA7endfloat.cfg,
%%                                 Figure1.pdf,
%%                                 shortsample.tex,
%%                                 longsample.tex, and
%%                                 bibliography.bib.
%% 
%%
%% End of file `./samples/longsample.tex'.